A fast unified model for parsing and sentence understanding

### 2016-03-15 writing/hard_stack_paper/paper.tex
Update results with better numbers (rerun on jag10)

We implemented the feedforward of the SPINN-NP-NT model (which is equivalent to a standard TreeRNN) in C++/CUDA in order to compare to the performance of a standard CPU-based TreeRNN solution \cite{irsoy2014deep}. Figure~\ref{fig:speed} compares the runtime performance of the two models computing representations on data from the Stanford Sentiment Treebank \todo{cite}. Each model is restricted to run on sentences of 30 tokens or fewer (for the SPINN model, this means we iterate over a sequence of 61 transitions \todo{[JG] Not 59?}). We fix the model dimensionality and word embedding dimensionality at 300 for all tests. \todo{[JG] Explain why we implemented *just* feedforward in this style. (Something like: Theano is convenient for training but very non-optimal for our model.)}

>>>>

We implemented the feedforward of the SPINN-NP-NT model (which is equivalent to a standard TreeRNN) in C++/CUDA in order to compare to the performance of a standard CPU-based TreeRNN solution \cite{irsoy2014deep}. Figure~\ref{fig:speed} compares the runtime performance of the two models computing representations on data from the Stanford Sentiment Treebank \todo{cite}. Each model is restricted to run on sentences of 30 tokens or fewer (for the SPINN model, this means we iterate over a sequence of 59 transitions. We fix the model dimensionality and word embedding dimensionality at 300 for all tests. \todo{[JG] Explain why we implemented *just* feedforward in this style. (Something like: Theano is convenient for training but very non-optimal for our model.)}
